OwO

### 2020-01-28 msc_english_contents.tex
Add LeNet

\chapter{Tasks}
What has been done when solving these tasks/history/formal definition
\section{Image classification}
Image classification is one of the basic modern computer vision problems, where the goal is to create a model that can classify an input image into one of a set of pre-defined classes. Prior to the popularization of applying large Convolutional Neural Networks for this task, the most successful way of solving the problem was to use some algorithm for finding feature descriptors in a set of images and then training a linear classifier, like a Support Vector Machine over a Visual Bag of Words representation of the images. These days nearly all approaches are based on using deep CNNs.
\subsection{ImageNet}
ImageNet  \citep{imagenet}  is perhaps the most significant dataset for image classification and especially the ImageNet Challenge \citep{ILSVRC}, which is a challenge for a collection of 1000 classes from the ImageNet dataset for image classification using 1.2 million training and 150 thousand  images of the entire ImageNet dataset. In 2012 the winning model, AlexNet \citep{alexNet}, showed that it was possible to train a deep CNNs efficiently using GPUs. Since 2012 all top-performing models showed some new improvements on how to create the most performant network architecture, for example, VGGNet from the year 2014 and ResNet \citep{resNet} from 2015, both of which have been popular models to use for Transfer Learning since.

>>>>

\chapter{Tasks}
What has been done when solving these tasks/history/formal definition
\section{Image classification}
Image classification is one of the essential modern computer vision problems, where the goal is to create a model that can classify an input image into one of a set of pre-defined classes. Before the popularization of applying large Convolutional Neural Networks for this task, the most successful way of solving the problem was to use some algorithm for finding feature descriptors in a set of images to construct a Visual Bag of Words.  A linear classifier, like a Support Vector Machine, would then do the classification using the Bag of Words representation of an image. These days nearly all approaches are based on using deep CNNs, and working CNNs were deployed already in 1998 on character recognition in the form of LeNet \citep{leNet}.
\subsection{ImageNet}
ImageNet  \citep{imagenet}  is perhaps the most significant dataset for image classification and especially the ImageNet Challenge \citep{ILSVRC}, which is a challenge for a collection of 1000 classes from the ImageNet dataset for image classification using 1.2 million training and 150 thousand  images of the entire ImageNet dataset. In 2012 the winning model, AlexNet \citep{alexNet}, showed that it was possible to train a deep CNNs efficiently using GPUs. Since 2012 all top-performing models showed some new improvements on how to create the most performant network architecture, for example, VGGNet from the year 2014 and ResNet \citep{resNet} from 2015, both of which have been popular models to use for Transfer Learning since.
